### 2019-08-21 Manuscript/Manuscript.tex
Updates from Overleaf

@@

\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{Park et al., in preparation for XXX}
\rhead{\thepage}

@@

Yuem Park\textsuperscript{1},
Nicholas L. Swanson-Hysell\textsuperscript{1},
Pierre Maffre\textsuperscript{1},
Francis A. Macdonald\textsuperscript{2},
Yves Godd\'eris\textsuperscript{3}

@@

\noindent\textit{This article is in preparation for XXXX}

@@

\section*{ABSTRACT \label{sec:ABSTRACT}}

\section*{INTRODUCTION \label{sec:INTRODUCTION}}

@@

\section*{METHODS}

\subsection*{Paleoshoreline data}

@@

While the overall picture of the region is an increase in land area, there is a decrease in land area associated with subsidence of the Sunda Shelf. Although the majority of the Sunda Shelf is currently submerged, large portions of this low-relief area of continental crust were likely emergent throughout the Neogene, and were repeatedly subaerially exposed during the Pleistocene as recently as the Last Glacial Maximum \citep{Halls2002a}. Similarities in terrestrial biotas of Borneo and mainland Southeast Asia suggest the existence of land bridges on the Sunda Shelf throughout the Miocene \citep{Moss1998a}. During the Eocene through early Miocene, the rifting of the South China Sea resulted in subsidence throughout the Sunda Shelf \citep{Morley2013a}. In the Miocene, this region was likely a mixture of crystalline lithologies and siliciclastic sediments. This low-relief region contrasts with the high-relief and mafic lithologies of the broader Indonesia archipelago.

>>>>

% Letters
% Letters are short reports of original research focused on an outstanding finding whose importance means that it will be of interest to scientists in other fields.

% They do not normally exceed 4 pages of Nature and, as a guideline, allow up to 30 references. They begin with a fully referenced paragraph, ideally of about 200 words, but certainly no more than 300 words, aimed at readers in other disciplines. This paragraph starts with a 2-3 sentence basic introduction to the field; followed by a one-sentence statement of the main conclusions starting 'Here we show' or equivalent phrase; and finally, 2-3 sentences putting the main findings into general context so it is clear how the results described in the paper have moved the field forwards.

% Please refer to our annotated example to see how the summary paragraph for a Letter should be constructed.

% The rest of the text is typically about 1,500 words long. Any discussion at the end of the text should be as succinct as possible, not repeating previous summary/introduction material, to briefly convey the general relevance of the work.

% Letters typically have 3 or 4 small display items (figures or tables).

% Word counts refer to the text of the paper. References, title, author list and acknowledgements do not have to be included in total word counts.

@@

\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{Park et al., in preparation}
\rhead{\thepage}

@@

Yuem Park\textsuperscript{1},
Nicholas L. Swanson-Hysell\textsuperscript{1},
Pierre Maffre\textsuperscript{1},
Francis A. Macdonald\textsuperscript{2},
Eliel A. Anttila\textsuperscript{2},
Yves Godd\'eris\textsuperscript{3}

@@

@@

@@

% \section*{METHODS}

% \subsection*{Paleoshoreline data}

@@

While there has been an increase in land area associated with arc-continent, there is a decrease in land area associated with subsidence of the Sunda Shelf \citep{Sarr2019a}. Although the majority of the Sunda Shelf is currently submerged, large portions of this low-relief area of continental crust were likely emergent throughout the Neogene, and were repeatedly subaerially exposed during the Pleistocene as recently as the Last Glacial Maximum \citep{Halls2002a}. Similarities in terrestrial biotas of Borneo and mainland Southeast Asia suggest the existence of land bridges on the Sunda Shelf throughout the Miocene \citep{Moss1998a}. During the Eocene through early Miocene, the rifting of the South China Sea resulted in subsidence \citep{Morley2013a} and recent subsidence is interpretted to be a result of dynamic topography, triggered by subduction-related mantle flow \citep{Sarr2019a}. In the Miocene, this region was likely a mixture of crystalline lithologies and siliciclastic sediments similar to eastern Borneo. The relatively low-relief of the region contrasts with the high-relief and mafic lithologies of the broader Indonesia archipelago. We incorporate land area associated with the subsided Sunda shelf into our modeling.
